\href{https://dl.acm.org/doi/10.1145/3484577}{Lu, S., et al. "CodeXGLUE: A Benchmark Dataset for Code Intelligence." ACM Transactions on Software Engineering and Methodology (2021)}.


\href{https://arxiv.org/abs/2203.04225}{Zhu, M., et al. "XLCoST: A Benchmark Dataset for Cross-Language Code Snippet Transfer." arXiv:2203.04225 (2022)}.


\href{https://arxiv.org/abs/1909.09436}{Husain, H., et al. "CodeSearchNet Challenge: Evaluating the State of Semantic Code Search." arXiv:1909.09436 (2019)}


\begin{thebibliography}{9}
    \bibitem[Zhu et al., 2022]{zhu2022} Zhu, M., et al. "XLCoST: A Benchmark Dataset for Cross-Language Code Snippet Transfer." arXiv:2203.04225 (2022).
    \bibitem[Chen et al., 2023]{chen2023} Chen, Y., et al. "On the Reliability of Code Summarization Benchmarks." IEEE Transactions on Software Engineering (2023).
    \bibitem[Rепозиторий XLCoST]{repo} Репозиторий XLCoST: \url{https://github.com/XLCOST/} (файлы \texttt{python\_code\_to\_text.jsonl}, \texttt{cross\_lang\_pairs.csv}).
    \end{thebibliography}

    \subsection{Ссылки}
    \begin{enumerate}
        \item Ren, S., et al. "CodeBLEU: A Method for Evaluating the Quality of Code Summarization." ICSE (2021).
        \item Zhang, T., et al. "BERTScore: Evaluating Text Generation with BERT." arXiv:1904.09675 (2020).
        \item https://habr.com/ru/articles/745642/
        \item https://github.com/google-research/bleurt
        \item Feng et al. (2023) — исследование по BERTScore.
        \item Husain et al. (2019) — работа по ROUGE для Go.
    \end{enumerate}

    \subsection{Ссылки}
\begin{thebibliography}{9}
\bibitem[CodeSearchNet]{codesearchnet} Husain et al., "CodeSearchNet: A Benchmark for Code Retrieval", 2019, \url{https://arxiv.org/abs/1909.09436}.
\bibitem[CodeXGLUE]{codexglue} Lu et al., "CodeXGLUE: A Benchmark for Code Understanding and Generation", 2021, \url{https://arxiv.org/abs/2102.04664}.
\bibitem[XLCoST]{xlcost} Zhu et al., "XLCoST: Cross-Language Code Snippet Transfer", 2022, \url{https://arxiv.org/abs/2203.04225}.
\bibitem[CodeSearchNet Repo]{codesearchnet_repo} Репозиторий CodeSearchNet: \url{https://github.com/github/CodeSearchNet}.
\bibitem[CodeXGLUE Repo]{codexglue_repo} Репозиторий CodeXGLUE: \url{https://github.com/microsoft/CodeXGLUE}.
\end{thebibliography}
